### 2018-03-26 tex/paper.tex
Add references to Blockly, Haste, and version 1.2

The tool has been mainly written in Haskell and compiled to JavaScript
by the Haste compiler \plsnote{Citation needed}, it also relies on
the Blockly library \plsnote{Citation needed} for providing a visual
editor for smart contracts written in Marlowe. Blockly's editor allows
the user to visualise and edit smart-contracts as interlocking blocks
that can be dragged and dropped like pieces of a jigsaw puzzle (see
Figure~\ref{fig:detail-of-block}). The tool also provides functionality
to generate syntactically correct and formatted code (that is displayed
in the upper right corner of the application), and to convert the
code back to its block representation.

@@

We have given a concrete model and DSL, namely Marlowe version 1.2. In this section we examine how the model can be 
extended, how contacts can be analysed, reflect on different design decisions that might be made and discuss some 
aspects of the implementation of Marlowe within a blockchain environment.

>>>>

The tool has been mainly written in Haskell and compiled to JavaScript
by the Haste compiler \cite{Haste}, it also relies on
the Blockly library \cite{Blockly} for providing a visual
editor for smart contracts written in Marlowe. Blockly's editor allows
the user to visualise and edit smart-contracts as interlocking blocks
that can be dragged and dropped like pieces of a jigsaw puzzle (see
Figure~\ref{fig:detail-of-block}). The tool also provides functionality
to generate syntactically correct and formatted code (that is displayed
in the upper right corner of the application), and to convert the
code back to its block representation.

@@

We have given a concrete model and DSL, namely Marlowe version 
1.2\footnote{\url{https://github.com/input-output-hk/scdsl/releases/tag/v1.2}}.
In this section we examine how the model can be extended, how contacts can be analysed, reflect on different design 
decisions that might be made and discuss some aspects of the implementation of Marlowe within a blockchain environment.
